\vspace*{-2.5cm} \hspace*{-0.5cm}Online platformazation and Offline expansion of Real Estate Brokerage: Evidence from China\footnote{ We are grateful for various people from various university, and several conferences for useful feedback. }

### 2024-06-08 manuscript/main.tex
modified:   manuscript/main.aux 	modified:   manuscript/main.fdb_latexmk 	modified:   manuscript/main.log 	modified:   manuscript/main.pdf 	modified:   manuscript/main.synctex.gz 	modified:   manuscript/main.tex

In this paper, we empirically estimate the offline stores' , the brokerages can earn higher income in this community, and we decompose the channels into two parts. On the one hand, is that when brokers have better control over listing information by opening additional offline stores, they are more likely to attract more sellers to choose them, which will then benefited by the online platform effect to extract more buyers and more likely to complete a transaction. On the other hand, when offline stores are closer to the communities, they are more likely to make a house tour to help the buyers to get more information on the house, and therefore, be more likely to complete a transaction. During the Covid-19 pandemic period, the Chinese government restricts the number, and in this period, we find that the number of houses tour is not significantly affected by the number of offline stores, but the listing information significantly decreases because the brokerages are difficult to interact with the sellers and then failure to maintain the information advantage during this period.

Apart from directly measuring the dynamic effect of Lianjia's offline stores to transaction, we use Lianjia's entry into the local segmented market as an exogenous shock to test the effect of entry on transaction characteristics. The results indicate that when Lianjia enters the market, revenues increase significantly, but this is not due to the larger clinic-based, but due to the greater information control brought by the newly opened store. Moreover, during pandemic periods, we find that all effects are diminished, meaning that during pandemic periods, both the client-based effect and the housing information are diminished. Simultaneously, our study also examines the impact of Lianjia's ACN strategy on the real estate market, focusing on its effect on offline store operations. Through this exogenous shock, we find that post-2018, the ACN significantly boosts revenue and alters consumer behaviors, especially in terms of price concessions and house tours. Also, contrary to the previous effect, the effects are diminished during pandemic periods. The findings highlight the resilience of physical stores during a global epidemic and underscore the necessity for a synergistic evolution of online and offline strategies.

The remainder of the paper proceeds as follows. Section \ref{sec:literature_review} reviews the literature that is related to our research. Section \ref{sec:data} describes the data and summarizes the statistical evidence. Section \ref{sec:theoretical_model} presents a theoretical model that incoporate the analysis. Section \ref{sec:mechanism_design} presents the main result of our finding. Finally, Section \ref{sec:conclusion} concludes.

>>>>

In this paper, we empirically estimate the effects of offline store clustering and online platform consolidation in China's second-hand real estate market. Utilizing micro-level transaction data, we construct our research sample by aggregating information at the neighborhood level. We employ a regression discontinuity (RD) design to identify the optimal influential radius of offline stores on neighborhood transactions, finding that this radius corresponds to a brokerage's five-minute walk service distance. Subsequently, we apply a difference-in-difference (DID) estimation method to evaluate the exogenous impact of Lianjia's market entry on local segments. This exogenous effect captures the clustering impact of offline real estate brokerage stores. Our results indicate that Lianjia's offline stores significantly enhance transaction revenues, although this effect diminishes during and after the COVID-19 period.

To assess the consolidation effect of the online platform, we treat the year Lianjia implemented the Agent Cooperate Network (ACN) strategy as an exogenous shock to the market. Our findings reveal that this strategy substantially boosts revenues and alters consumer behaviors, particularly in the number of house tours facilitated by the brokerage. These results underscore the necessity for a synergistic evolution of online and offline strategies in the real estate brokerage market. Furthermore, they indicate that the online consolidation effect is becoming increasingly significant relative to the offline clustering effect.

Our research has several implications. Firstly, it indicates that with the advent of new technologies, the online consolidation effect is becoming increasingly important for real estate companies. This shift underscores the need for firms to enhance their digital strategies to remain competitive. Secondly, our findings have broader significance for other industries where online consolidation can potentially replace traditional offline clustering. For example, in the retail sector, online marketplaces such as Alibaba in China have significantly outpaced physical stores by consolidating various vendors into a single, accessible platform.

By examining these dynamics, our research contributes to a deeper understanding of the evolving landscape of real estate brokerage in China. It provides valuable insights for policymakers and industry stakeholders aiming to enhance market efficiency and competitiveness. As the online consolidation effect continues to grow, our findings highlight the importance of adapting to this trend and evolving strategies accordingly. Specifically, transitioning from a bilateral brokerage model to a model where buyer and seller agencies are separated could be crucial for sustaining a competitive advantage in the real estate brokerage market. This strategic shift entails leveraging online platforms to integrate services and enhance transaction efficiency, thereby benefiting both consumers and firms. By disentangling the roles of buyer and seller agents, the market can reduce conflicts of interest, increase transparency, and improve overall market efficiency. This alignment with economic principles of specialization and efficiency further underscores the potential for significant gains in consumer welfare and firm profitability.

The remainder of the paper proceeds as follows. Section \ref{sec:literature_review} reviews the literature that is related to our research. Section \ref{sec:data} describes the study background and the data source. Section \ref{sec:statistical} describes the statistical summary and other relevant information. Section \ref{sec:mechanism_design} presents the main result of our finding. Finally, Section \ref{sec:conclusion} concludes.
